### 2023-06-24 manuscript.tex
html rendering [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/f697e5dfb9f4502a9486a03fbf56a5d69e0a6b56.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/f697e5dfb9f4502a9486a03fbf56a5d69e0a6b56/checks
https://github.com/stain/2022-fdo-paper/actions/runs/5366467035

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/9677b4fb32c5e4e6351e27304de42c115a379172/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/9677b4fb32c5e4e6351e27304de42c115a379172}{stain/2022-fdo-paper@9677b4f}
on June 24, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/f697e5dfb9f4502a9486a03fbf56a5d69e0a6b56/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/f697e5dfb9f4502a9486a03fbf56a5d69e0a6b56}{stain/2022-fdo-paper@f697e5d}
on June 24, 2023.
